Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-02-10 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Finished eqs

\begin{frame}
\frametitle{?}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2010, 2019): Business practices, motivation \citep{Bloom2010, Bloom2019}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Heterogeneity in Business Practices}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2010): Heterogeneity \citep{Bloom2010}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Business Practices and Performance}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2019): Correlation with productivity \citep{Bloom2019}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

		\item 4 major domains of business practices
		\begin{enumerate_2pt}
			\item Book-keeping and accounting
			\item Financial planning
			\item Inventory management and stock control
			\item Marketing
		\end{enumerate_2pt}
	\item[] $\rightarrow$ \textcolor{bdf}{Vast heterogeneity} in business practices \citep[comp.][]{Bloom2010}
	\item[] $\rightarrow$ \textcolor{bdf}{Robust association with performance and firm survival} across industries and contexts
	\item[] $\rightarrow$ \textcolor{bdf}{Strong persistent component} one year out ($r=0.59$)
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Business Practices in Small Firms}
	\citet{McKenzie2017} identify set of XX practices most closely associated with business performance
	\begin{itemize_2pt}
		\item Example practices:
		\begin{enumerate_2pt}
			\item e.g., 
			\item e.g., 
			\item e.g., 
			\item e.g.,  
		\end{enumerate_2pt}
	\end{itemize_2pt}

@@

	Open questions
	\begin{itemize_2pt}
		\item Does adoption of "best practices" \emph{cause} performance to increase?
		\item How can adoption of practices best be encouraged?
	\end{itemize_2pt}
\end{frame}

>>>>

\begin{frame}
\frametitle{Heterogeneity in Business Practices}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2010, 2019): Business practices, motivation \citep{Bloom2010, Bloom2019}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Heterogeneity in Business Practices}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2010): Heterogeneity across mid-sized and large firms \citep{Bloom2010}
	\end{itemize_2pt}
\end{frame}

@@

		\item 4 major domains of business practices
		\begin{enumerate_2pt}
			\item Book-keeping and accounting
			\item Financial planning
			\item Inventory management and stock control
			\item Marketing
		\end{enumerate_2pt}
	\item[] $\rightarrow$ \textcolor{bdf}{Vast heterogeneity} in business practices \citep[comp.][]{Bloom2010}
	\item[] $\rightarrow$ \textcolor{bdf}{Strong persistent component} one year out ($r=0.59$)
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Business Practices in Small Firms}
	\citet{McKenzie2017} identify set of XX practices most closely associated with business performance
	\begin{itemize_2pt}
		\item Example practices:
		\begin{enumerate_2pt}
			\item e.g., 
			\item e.g., 
			\item e.g., 
			\item e.g.,  
		\end{enumerate_2pt}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Business Practices in the Production Decision}

Standard Production Decision
	\begin{itemize_2pt}
		\item Owner maximizes output $Y = f(\textcolor{red}{A}, \textcolor{bdf}{L, M, K})$ at given wealth $\textcolor{red}{W}$:

		\item[] $\boxed{ \begin{aligned} \max _{\textcolor{bdf}{K, M, L}} &\{\textcolor{red}{p} \text{ } f(\textcolor{red}{A}, \textcolor{bdf}{L, M, K})-\textcolor{red}{w} \textcolor{bdf}{L}-\textcolor{red}{s} \textcolor{bdf}{M}-\textcolor{red}{r} \textcolor{bdf}{K}\} \end{aligned} }$
		\item[] $\boxed{ \begin{aligned} \text{s.t.} &\ \textcolor{red}{w} \textcolor{bdf}{L}+\textcolor{red}{s} \textcolor{bdf}{M}+\textcolor{red}{r} \textcolor{bdf}{K} \leq \textcolor{red}{\lambda} \textcolor{red}{W} \end{aligned} }$

		\begin{itemize_2pt}
			\item[] .. where $\textcolor{bdf}{L}$ is labor, $\textcolor{bdf}{M}$ is materials, and $\textcolor{bdf}{K}$ is capital.
			\item[] .. where $\textcolor{red}{p}$ is the output price, $\textcolor{red}{w}$ the cost of labor, $\textcolor{red}{s}$ the cost of raw materials, and $\textcolor{red}{r}$ cost of capital
			\item[] .. where $\textcolor{red}{A}$ represents a productivity factor and \textcolor{red}{$\lambda$} parameterizes borrowing constraints
		\end{itemize_2pt}

		\item 2 general conceptualizations of business practices
		\begin{enumerate_2pt}
			\item As factor of production $\textcolor{bdf}{B}$ chosen by owner at market price $\textcolor{red}{p_{B}}$
			\item As technology boosting productivity factor $\textcolor{red}{A}$
			\item[] \citep[see,][]{Bloom2016, McKenzie2017}
		\end{enumerate_2pt}

	%\item Bloom et al. (2016) Bloom N, Sadun R, Van Reenen J (2016) Management as a technol- ogy? NBERWorking Paper 22327, National Bureau of Economic Research, Cambridge, MA.
	%\item McKenzie2017 3.1.
	\end{itemize_2pt}

\begin{frame}
\frametitle{Business Practices in the Production Decision}

Further specific channels of impact
\begin{enumerate_2pt}
	\item Better negotiation practices may affect raw material prices $\textcolor{red}{s}$
	\item Record-keeping and financial planning practices may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend
	\item Marketing practices may affect output price $\textcolor{red}{p}$ by changing demand

	\item[] $\rightarrow$ Plausible association between business practices and revenues, profits, and business growth
	\item[] $\rightarrow$ Prices ($\textcolor{red}{p}$, $\textcolor{red}{s}$, and $\textcolor{red}{p_{B}}$) and inputs ($\textcolor{bdf}{K}$, $\textcolor{bdf}{L}$, and $\textcolor{bdf}{M}$) likely endogenous to business practices $\textcolor{bdf}{B}$
\end{enumerate_2pt}

\begin{frame}
\frametitle{Business Practices and Performance}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2019): Correlation with productivity across mid-sized and large firms \citep{Bloom2019}
	\item McKenzie2017: \textcolor{bdf}{Robust association with performance and firm survival} across industries and contexts in small firms
	\end{itemize_2pt}

@@

	Open questions
	\begin{itemize_2pt}
		\item Does adoption of "best practices" \emph{cause} performance to increase?
		\item How can adoption of practices best be encouraged?
	\end{itemize_2pt}
